---
title: "An example of implementing the code"
author: "Xiuwen Duan, Mayer Alvo"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Given a list of observed samples, we generate the compatible sets for each observation in this sample. Then use the compatible set to estimate the full ranking for the observations. 

Firstly, suppose we are given in observations of 4 incomplete rankings: (you can input your own data here)
```{r }
observation<-matrix(c(1,2,3,4,0,
                      1,3,2,0,0,
                      4,2,0,3,1,
                      0,0,3,2,1),4,5,byrow=T)
```

Alternatively, one can import the data from a csv or txt file.
```{r }
observation<-as.matrix(read.csv("observation1.csv",header=FALSE))
observation<-as.matrix(read.table("observation2.txt"))
```

Then, we load the algorithms to generate the compatible set.
```{r }
source("Compatible.R")
```

Use the function "two_stage_complete" to generate compatible sets.
```{r }
Compatible<-list()
for(i in 1:nrow(observation)){
  Compatible[[i]]<-Two_stage_complete(observation[i,])
}
```

So the compatible set now contains n=3 matrices each contains all permutations for each of above rankings.
```{r }
Compatible
```

Next, we standardize the data.
```{r}
t<-ncol(observation)
for(i in 1:nrow(observation)){
  Compatible[[i]]<-Compatible[[i]]-mean(c(1:t))
  mod<-sqrt(t*(t^2-1)/12)
  Compatible[[i]]<-Compatible[[i]]/mod
}
```

Then we load the EM algorithm and make estimates with a specified stopping criterion. It will give us result of the mean vector $\mu$, normalizing parameter $\kappa$, and the probability of the predicted $\mu$. We set the stopping parameter $\epsilon$ to be 0.1 to avoid computational problems when running too many times. 
```{r }
source("EM.R")
result<-EM(observation,Compatible,0.1,20)
result
```

In the end, we can rank the mean vector to see the predicted overall ranking of this sample.
```{r }
rank(result$mu)
```
